\hypertarget{index_Installation}{}\section{Installation}\label{index_Installation}
This has been compiled for Mac OS X 10.7 as an application. Source code is where its at and its available for download at: \href{https://github.com/tareiking/xbeeChoice}{\tt github} to compile yourself.\hypertarget{index_install_sec}{}\section{Usage}\label{index_install_sec}
\hypertarget{index_step1}{}\subsection{Step 1: Connect xbee}\label{index_step1}
This application gets information from what ever is in port 0. If your xbee + uart is not connected there is no error checking to tell you so. Apart from absolute failure.\hypertarget{index_step2}{}\subsection{Step 2: Run application}\label{index_step2}
\hypertarget{index_step3}{}\subsection{Step 3: In app}\label{index_step3}
'SPACEBAR' enters command mode: You will need to be quick. By default you have 3 seconds before it automatically logs you out of command mode 'MOUSE CLICK' chooses parameters to change on the xbee 'ENTER' to send command to xbee.\hypertarget{index_step4}{}\subsection{Note: Your messages should automatically be appended to the previous command. If its looking weird, roll your own message!}\label{index_step4}
\hypertarget{index_step5}{}\subsection{Step 4: Roll your own}\label{index_step5}
If the built in messages aren't enough you can either type the commands manually on screen or create / edit the x.bee file (which is just valid xml)\hypertarget{index_Video}{}\section{Video}\label{index_Video}
See it in action :) $<$iframe width=\char`\"{}420\char`\"{} height=\char`\"{}315\char`\"{} src=\char`\"{}http://www.youtube.com/embed/kjBralkAkjM\char`\"{} frameborder=\char`\"{}0\char`\"{} allowfullscreen$>$=\char`\"{}\char`\"{}$>$$<$/iframe$>$ 